---
params:
  symbol: "TSLA"
title: Stock Price Import for `r params$symbol`
output: html_document
rmd_output_metadata:
  rsc_output_files:
    - "prices.csv"
---

`r if(Sys.getenv('CONNECT_SERVER') == '') { "ERROR: You must set the CONNECT_SERVER environment variable\n" }`
`r if(Sys.getenv('CONNECT_API_KEY') == '') { "ERROR: You must set the CONNECT_API_KEY environment variable\n" }`
`r if(Sys.getenv('CONNECT_API_KEY') == '' || Sys.getenv('CONNECT_SERVER') == '') { knitr::knit_exit() }`

```{r, include=FALSE, message=FALSE, warning=FALSE}
library(dplyr)
library(stringr)
library(magrittr)
library(quantmod)
library(ggplot2)
library(pins)

start_time <- Sys.time()

# Fetch all pricing data for symbol
prices <- getSymbols(params$symbol,
                     from = as.Date("2001-01-01"),
                     to = Sys.Date(),
                     src="yahoo",
                     auto.assign = FALSE)
  
dates <- index(prices)
  
# Convert to format: symbol, date, open, close, high, low, volume
prices %<>%
  as_tibble %>%
  mutate(symbol = params$symbol, date = dates) %>%
  rename_at(
    vars(starts_with(params$symbol)), 
    list(~ str_replace(., paste(params$symbol, ".", sep = ""), ""))
  ) %>%
  rename_all(tolower) %>%
  select(symbol, date, "open", "close", "high", "low", "volume")

end_time <- Sys.time()
```

- **Started:** `r start_time`
- **Completed:** `r end_time` (`r difftime(end_time, start_time, units = "secs")`s)
- **Imported:** `r nrow(prices)` daily prices for **`r params$symbol`** from `r first(prices$date)` to `r last(prices$date)`

```{r, echo=FALSE}
prices %>% ggplot() +
  aes(x = date, y = close) +
  geom_line(color = "salmon") +
  labs(x = "Date", y = "Closing Price") +
  theme_minimal()
```

#### Data

```{r, include=FALSE}
write.csv(prices, "prices.csv", row.names=FALSE)

# Pins will use CONNECT_API_KEY and CONNECT_SERVER by default,
# but we are being explicit here anyway.
board_register("rsconnect",
               key = Sys.getenv("CONNECT_API_KEY"),
               server = Sys.getenv("CONNECT_SERVER"))

pin_name <- paste("prices-", params$symbol, sep = "")

pin(prices, pin_name, board = "rsconnect")

pin_meta <- pin_find(pin_name, board = "rsconnect")
```

- CSV: [prices.csv](prices.csv)
- Pin: ``r pin_meta$name``

**Note:** The pinned data can be fetched elsewhere using the following code

    library(pins)
    
    board_register("rsconnect",
                   key = Sys.getenv("CONNECT_API_KEY"),
                   server = Sys.getenv("CONNECT_SERVER"))

    prices <- pin_get('`r pin_meta$name`', board = "rsconnect")
